Significant wind disturbances induced by giant dunes.

### 2021-11-26 Paper/main.tex
Clean start for the diffrenet branches

Whenever a flow encounters an obstacle, various types of interactions can arise depending the different time and lengths scales involved. In the case of atmospheric flows, this depends mainly on the part of the vertical structure of the atmosphere, schematically composed of a turbulent boundary layer topped by a turbulence-free part, with which the obstacle interacts.
%
At the largest scale, the feedback of mountains on the stratified flow of the free atmosphere results in wave generation as well as significant wind disturbances, such as foehn winds in the lee side \citep{refs}. Inside the boundary layer, the interaction between a turbulent flow and hilly surfaces is for example key to the understanding ocean surface wind-driven waves, or eolian beforms in desert \citep{Belcher1998, Sullivan2010, Courrech2015}.

>>>>

Whenever a flow encounters an obstacle, various types of interactions can arise depending the different time and lengths scales involved. In the case of atmospheric flows, this depends mainly on the part of the vertical structure of the atmosphere, schematically composed of a turbulent boundary layer topped by a turbulence-free part, with which the obstacle interacts \citep{Stull1988}.
%
At the largest scale, the feedback of mountains on the stratified flow of the free atmosphere results in wave generation as well as significant wind disturbances, such as foehn winds in the lee side \citep{refs}. Inside the boundary layer, the interaction between a turbulent flow and hilly surfaces is for example key to the understanding ocean surface wind-driven waves, or eolian beforms in desert \citep{Belcher1998, Sullivan2010, Courrech2015}.
